### 2014-10-15 fundamentals/intro.tex
improved discussion of background

This cycle has resulted in a a proliferation of specialized, limited-access 
fuel cycle simulators for the calculation of fuel cycle metrics, and methods 
for calculating those metrics vary among simulators. Some model the 
system of facilities, economics, and materials at static equillibrium, while 
others capture its dynamics.  
Similarly, while some simulators discretely model material and facilities, 
others treat materials in streams and facilities in fleets, in an aggregated 
fashion. Depending on their intended use, simulators often overspecialize, 
modeling a single aspect of the fuel cycle in great detail while neglecting 
others. A simulator created for policy modeling might have excellent 
capability in economics while material isotopics and transmutation detail are 
neglected.

When the \Cyclus simulator arose out of the 
\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code
was the result of lessons-learned from an \gls{LDRD} project at 
\gls{INL}, 
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} which 
captured regional behaviors in fuel cycle scenarios.

\Cyclus is a dynamic simulator that treats both materials and facilities discretely, with an 
architecture that permits simulations with multiple and variable levels of 
fidelity. Its agent-based framework for simulation and tracking of 
transformation and trade of resources between facilities within institutions 
and regions greatly improves upon the existing field of fuel cycle simulators.

Associated with \Cyclus is Cycamore (the additional modules repository).

>>>>

This cycle has resulted in a a proliferation of specialized
fuel cycle simulators for the calculation of fuel cycle metrics.  Accordingly, methods 
for calculating those metrics vary among simulators. Some model the 
system of facilities, economics, and materials at static equillibrium, while 
others capture its dynamics.  
Similarly, while some simulators discretely model material and facilities, 
others treat materials in streams and facilities in fleets, in an aggregated 
fashion. Depending on their intended use, simulators often overspecialize, 
modeling a single aspect of the fuel cycle in great detail while neglecting 
others. A simulator created for policy modeling might have excellent 
capability in economics while material isotopics and transmutation detail are 
neglected.

Accordingly, the \gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code
was created to provide and extensible interface to facilitate collaboration. 
The \gls{GENIUSv2} project relied on lessons-learned from an \gls{LDRD} project 
at \gls{INL}, 
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}.

The \Cyclus project, in turn, improved upon the \gls{GENIUSv2} project by 
implementing increased modularity and encapsulation.
The result is  a dynamic simulator that treats both materials and facilities 
discretely, with an architecture that permits simulations with multiple and 
variable levels of fidelity. Its agent-based framework for simulation and 
tracking of transformation and trade of resources between facilities within 
institutions and regions greatly improves upon the existing field of fuel cycle 
simulators.
